\bf Model Visualization Techniques for a Social Network Model

### 2017-09-19 paper.Rnw
fix compilation error

<<sigtesting, fig.show = 'hold', out.width='\\textwidth', fig.height=3, fig.cap="Significant effects for the two data sets, at the level of $\alpha = 0.10$ as calculated by the Wald-type test available in the \texttt{RSiena} software.">>=
smfr_effs <- read_csv("data/effects_significance_smallFriends.csv")
smfr_effs$inter1[is.na(smfr_effs$inter1)] <- "none"
library(ggrepel)
set.seed(12345678)
smfr_effs %>% filter(type == "eval" & Waldpval <=0.10) %>% 
ggplot(aes(x = estimate, y = Waldpval, color = inter1)) + 
  #geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +  
  geom_vline(xintercept = 0) + 
  geom_point(size = 3) + 
  geom_text_repel(aes(label = shortName)) + 
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") + 
  ggtitle("Significant effects at level 0.10 for friendship data") + 
  coord_flip() + 
  ThemeNoNet
sen_effs <- read_csv("data/congress/senateModelSigEffects.csv")
#sen_effs$Waldpval <- parse_number(sen_effs$Waldpval)
sen_effs$inter1[is.na(sen_effs$inter1)] <- "none"
ggplot(data = sen_effs %>% filter(Waldpval <=0.10), aes(x = estimate, y = Waldpval, color = inter1)) + 
  # geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +  
  geom_vline(xintercept = 0) + 
  geom_point(size = 3) + 
  geom_text_repel(aes(label = shortName)) + 
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") + 
  ggtitle("Significant effects at level 0.10 for senate data") + 
  coord_flip() + 
  ThemeNoNet
@

>>>>

<<sigtesting, fig.show = 'hold', out.width='\\textwidth', fig.height=3, fig.cap="Significant effects for the two data sets, at the level of 0.10 as calculated by the Wald-type test available in the SIENA software.">>=
smfr_effs <- read_csv("data/effects_significance_smallFriends.csv")
smfr_effs$inter1[is.na(smfr_effs$inter1)] <- "none"
library(ggrepel)
set.seed(12345678)
smfr_effs %>% filter(type == "eval" & Waldpval <=0.10) %>% 
ggplot(aes(x = estimate, y = Waldpval, color = inter1)) + 
  #geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +  
  geom_vline(xintercept = 0) + 
  geom_point(size = 3) + 
  geom_text_repel(aes(label = shortName)) + 
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") + 
  ggtitle("Significant effects at level 0.10 for friendship data") + 
  coord_flip() + 
  ThemeNoNet
sen_effs <- read_csv("data/congress/senateModelSigEffects.csv")
#sen_effs$Waldpval <- parse_number(sen_effs$Waldpval)
sen_effs$inter1[is.na(sen_effs$inter1)] <- "none"
ggplot(data = sen_effs %>% filter(Waldpval <=0.10), aes(x = estimate, y = Waldpval, color = inter1)) + 
  # geom_errorbarh(aes(xmin = estimate - se, xmax = estimate + se), color = 'black') +  
  geom_vline(xintercept = 0) + 
  geom_point(size = 3) + 
  geom_text_repel(aes(label = shortName)) + 
  scale_color_brewer(palette = "Paired", name = "Interaction\nVariable") + 
  ggtitle("Significant effects at level 0.10 for senate data") + 
  coord_flip() + 
  ThemeNoNet
@
